MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
added table and images

\documentclass{acm_proc_article-sp}

\begin{document}

\title{MITM: Logging a Bluetooth Keyboard}

\numberofauthors{2} 
\author{
\alignauthor Kimberly Paterson\\
\affaddr{Cal Poly San Luis Obispo}\\
\email{klpaters@calpoly.edu}\\
\alignauthor Ryan Verdon\\
\affaddr{Cal Poly San Luis Obispo}\\
\email{rverdon@calpoly.edu}\\
}

@@

The benefit of attacking a keyboard in this way is having direct access to the data being imputed into the keyboard without the need for physical access to the device or the software on either the keyboard or device it's connected to. Additionally, if an attack can successfully execute a MITM attack by logging the keyboard input and then forwarding the data to the victim PC or tablet, the user may not even be aware that their data are compromized.

@@

\section{Executing the Attack}
To execute this attack, we used completely off-the-shelf hardware and software. The only custom software and hardware would be the incorporation of the Ubertooth device and plugin for Kismet.

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{graphicx}
\begin{document}
\title{MITM: Logging a Bluetooth Keyboard}
\numberofauthors{2} 
\author{
\alignauthor Kimberly Paterson\\
\affaddr{Cal Poly San Luis Obispo}\\
\email{klpaters@calpoly.edu}\\
\alignauthor Ryan Verdon\\
\affaddr{Cal Poly San Luis Obispo}\\
\email{rverdon@calpoly.edu}\\
}

@@

The benefit of attacking a keyboard in this way is having direct access to the data being imputed into the keyboard without the need for physical access to the device or the software on either the keyboard or device it's connected to. Additionally, if an attack can successfully execute a MITM attack by logging the keyboard input and then forwarding the data to the victim PC or tablet, the user may not even be aware that their data are compromised.

@@

\begin{figure}
\includegraphics[scale=0.5]{hcidump.jpg}
\caption{Sample \texttt{hcidump} dump data showing capital A}
\label{fig:mypic}
\section{Executing the Attack}
To execute this attack, we used completely off-the-shelf hardware and software. The only custom software and hardware would be the incorporation of the Ubertooth device and plugin for Kismet. 
\end{figure}
